Exception Handling Bug Hazards in Android

### 2015-09-24 SPRINGER_JOURNAL/msr_journal.tex
extended paper version

\begin{table}
  \centering
  \begin{tabular}{lr|lr}
    \hline
     \multicolumn{2}{c}{\bfseries{GitHub}} &  \multicolumn{2}{c}{\bfseries{Google Code}} \\
      \bfseries{Lable} &  \bfseries{\% Occurrences} &  \bfseries{Lable} &  \bfseries{\% Occurrences} \\
    \hline
empty &	54.24\% & Defect &	91.96\% \\
Defect &	39.56\%  & Enhancement  &	3.16\% \\
Enhancement &	0.57\% & Task	& 1.37\% \\
Support &	0.52\% & empty &	1.12\% \\
Problem &	0.36\% & StackTrace &	0.70\% \\
Others &	4.74\% &  Others &	1.68\% \\   
  \hline
  \end{tabular}
  \caption{Labels on issues including exception stack traces.}
  \label{tab:lables}
\end{table}

@@

\begin{table}
  \centering
  \begin{tabular}{rp{29em}}
    \hline
    \bfseries{Signaler} & \bfseries{Description} \\
    \hline
    \bfseries{android} & If the exception is thrown in a method defined in Android platform.\\
    \bfseries{app}     & If the exception is thrown in an method defined on an Android app.\\
    \bfseries{libcore} & If the exception is thrown in one of the core libraries reused by Android (e.g., org.apache.harmony, org.w3c.dom, sun.misc, org.apache.http, org.json, org.xml). \\
    \bfseries{lib}     & If the exception is thrown on a method that was not defined by any of the elements above.\\
    \hline
  \end{tabular}
  \caption{Sources of exceptions in Android}
  \label{tab:signalers}
\end{table}

@@

\begin{table*}
  \centering
%  \begin{tabular}{rcccccccc}
  \begin{tabular}{lrrrrrrrr}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects}} &  \multicolumn{2}{c}{\bfseries{Occurrences}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline

@@

\begin{table}
\centering
\begin{tabular}{lrr}
\hline
\bfseries{Concern} & \bfseries{\% Occurrences on stacks} \\
\hline
Programming logic (java.lang and util) & 52,0\%\\
Resources (IO, Memory, Batery) & 23,9\% \\
Security & 4,1\%\\
Concurrency & 2,9\% \\
Backward compatibility & 5,5\% \\
Specific Exceptions & 4,9\%\\
General (Error, Exception, Runtime) & 6,7\%\\
\hline
\end{tabular}
\caption{Identifying the concerns related to root exceptions}
\label{tab:tophundrend}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{lrrrrrr}
    \hline
    \bfseries{Root Type} & \bfseries{Android} & \bfseries{Libcore} & \bfseries{App} & \bfseries{Lib}  & \bfseries{All} & \bfseries{\%} \\
    \hline

@@

\begin{table}
\centering

@@

\begin{table*}
  \centering
  \begin{tabular}{llcccccc}
    \hline
    \bfseries{Wrapper Type}  &  \bfseries{Root Cause Type} &  \bfseries{Projects}  &  \bfseries{Occurrences} & \textsf{Android} & \textsf{Java/Libcore} & \textsf{Lib} & \textsf{App}  \\
    \hline

@@

 In previous work ~\cite{coelho2015}, we mined exception stack traces available on issues reported on several Android projects hosted in GitHub and Googlecode. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard the toy-programs and non-Android repositories. For each repository, we extract the developers whose email are registered on each repository. We emailed the developers and received 74 answers.

The majority of our respondents have more than XXX years of Java development experience (XXXXX%) and  considerable experience in Android development (XXXXX years)  (XXXXXX%).

\subsection{Data Analysis}

\subsection{Results}

@@

\subsubsection{Q1:How often developers deal with the exception handling code in Android development}

\subsubsection{Q1:How often developers deal with the exception handling code in Android development}

\subsubsection{Q1:How often developers deal with the exception handling code in Android development}

>>>>

\begin{table}
  \scriptsize
  \centering
  \begin{tabular}{lr|lr}
    \hline
     \multicolumn{2}{c}{\bfseries{GitHub}} &  \multicolumn{2}{c}{\bfseries{Google Code}} \\
      \bfseries{Lable} &  \bfseries{\% Occurrences} &  \bfseries{Lable} &  \bfseries{\% Occurrences} \\
    \hline
empty &	54.24\% & Defect &	91.96\% \\
Defect &	39.56\%  & Enhancement  &	3.16\% \\
Enhancement &	0.57\% & Task	& 1.37\% \\
Support &	0.52\% & empty &	1.12\% \\
Problem &	0.36\% & StackTrace &	0.70\% \\
Others &	4.74\% &  Others &	1.68\% \\   
  \hline
  \end{tabular}
  \caption{Labels on issues including exception stack traces.}
  \label{tab:lables}
\end{table}

@@

\begin{table}
  \centering
  \scriptsize
  \begin{tabular}{rp{29em}}
    \hline
    \bfseries{Signaler} & \bfseries{Description} \\
    \hline
    \bfseries{android} & If the exception is thrown in a method defined in Android platform.\\
    \bfseries{app}     & If the exception is thrown in an method defined on an Android app.\\
    \bfseries{libcore} & If the exception is thrown in one of the core libraries reused by Android (e.g., org.apache.harmony, org.w3c.dom, sun.misc, org.apache.http, org.json, org.xml). \\
    \bfseries{lib}     & If the exception is thrown on a method that was not defined by any of the elements above.\\
    \hline
  \end{tabular}
  \caption{Sources of exceptions in Android}
  \label{tab:signalers}
\end{table}

@@

\begin{table*}
  \tiny
  \centering
%  \begin{tabular}{rcccccccc}
  \begin{tabular}{lrrrrrrrr}
    \hline
    \bfseries{Root Exception} &  \multicolumn{2}{c}{\bfseries{Projects}} &  \multicolumn{2}{c}{\bfseries{Occurrences}} & \textsf{Android} & \textsf{Libcore} & \textsf{App} & \textsf{Lib} \\
    & \bfseries{\#} &  \bfseries{\%} & \bfseries{\# } & \bfseries{\% } &&&&\\
    \hline

@@

\begin{table}
\scriptsize
\centering
\begin{tabular}{lrr}
\hline
\bfseries{Concern} & \bfseries{\% Occurrences on stacks} \\
\hline
Programming logic (java.lang and util) & 52,0\%\\
Resources (IO, Memory, Batery) & 23,9\% \\
Security & 4,1\%\\
Concurrency & 2,9\% \\
Backward compatibility & 5,5\% \\
Specific Exceptions & 4,9\%\\
General (Error, Exception, Runtime) & 6,7\%\\
\hline
\end{tabular}
\caption{Identifying the concerns related to root exceptions}
\label{tab:tophundrend}
\end{table}

@@

\begin{table}
\scriptsize
\centering
\begin{tabular}{lrrrrrr}
    \hline
    \bfseries{Root Type} & \bfseries{Android} & \bfseries{Libcore} & \bfseries{App} & \bfseries{Lib}  & \bfseries{All} & \bfseries{\%} \\
    \hline

@@

\begin{table}
\scriptsize
\centering

@@

\begin{table*}
\scriptsize
  \centering
  \begin{tabular}{llcccccc}
    \hline
    \bfseries{Wrapper}  &  \bfseries{Root Cause} &  \bfseries{Projects}  &  \bfseries{Occurrences} & \textsf{Android} & \textsf{Java/Libcore} & \textsf{Lib} & \textsf{App}  \\
    \hline

@@

 In previous work~\cite{co15}, we mined exception stack traces available on issues reported on several Android projects hosted in GitHub and Googlecode. To ensure that our sample consists of repositories that were real Android apps, we had to inspect every project site and discard the toy-programs and non-Android repositories. For each repository, we extract the developers whose email are registered on each repository. We emailed the developers and received 74 answers.

The majority of our respondents have more than 2 years of Java development experience (87.3\%) and  considerable experience in Android development (more than 1 year)  (85.9\%) - see Figure~\ref{fig:devexpertise}.

\begin{figure} \centering \includegraphics[scale=0.35]{charts/Q1Q2.png}
\caption{Developers expertise in Java and Android development.}
\label{fig:devexpertise}
\end{figure}

\subsection{Findings}

@@

\noindent\emph{\textbf{Q1:How often developers deal with the exception handling code in Android development?}}

Many of our survey respondents said they have to handle exceptions most of the time during Android app development (64.8\%). However, the frequency on which they throw exception inside apps is smaller; most of the survey respondents said they throw exceptions only some of the time or seldom (80.3\%). It shows that although we can try to avoid dealing with exceptions throwing few exceptions, it is almost always inevitable to handle the exceptions thrown by Android platform and reused libraries.

\begin{figure} \centering \includegraphics[scale=0.35]{charts/Q3Q4.png}
\caption{How often.}
\label{fig:oftenhandle}
\end{figure}

\noindent\emph{\textbf{Q2: Do developers know about exception handling best practices?}}

We can observe that 62\% of surveyed Android developers follow Java exception handling best practices. Among the best practices cited by developers the most popular ones were: avoid generic catches and avoid empty catch blocks. They did not mention a any guide or reference of best practices. When asked about best practices specific to Android developers, most of the developers mentioned that they did no about them. The ones who answered positively said that they adopt the same best practices as in any Java program.

\begin{figure} \centering \includegraphics[scale=0.35]{charts/Q7Q8.png}
\caption{How often.}
\label{fig:oftenhandle}
\end{figure}

\noindent\emph{\textbf{Q3:What are the developers perspectives about the exception handling bug hazards?}}
